Hydraulically-vulnerable trees survive on deep-water access during droughts in a tropical forest

### 2021-04-09 09.0_manuscript.rmd
Added grid lines, added more axis breaks

\
For comparison with modelled ERD, we removed six species from the @Meinzer:1999 dataset to account for the uncertainty in their water-sourcing depths. $\mathrm{\delta}$^2^H~xylem~ from leafless trees may not be linked with water sourced at the time of measurement and thus may not be comparable to species that had leaves. Leaflessness status of sampled trees is not recorded in @Meinzer:2001. We therefore removed five species that are typically leafless in March-April (Joseph Wright, personal observation), that is, the months of $\mathrm{\delta}$^2^H~xylem~ sampling. $\mathrm{\delta}^2H$ to depth relationship was particularly uncertain for $\mathrm{\delta}^2H$ > -40 ‰, so from the remaining dataset, we removed one species, *Guapira standleyana*, with $\mathrm{\delta}$^2^H~xylem~ of -28.9 ‰ $\\pm$ 3.7SE (see Fig. S3). For each model of ERD (Eq. \@ref(eq:M-chosen) and alternatives in SI), modeled species ERD was regressed against species $\mathrm{\delta}$^2^H~xylem~ for a maximum of six species.

>>>>

\
For comparison with modelled ERD, we removed six species from the @Meinzer:1999 dataset to account for the uncertainty in their water-sourcing depths. $\mathrm{\delta}$^2^H~xylem~ from leafless trees may not be linked with water sourced at the time of measurement and thus may not be comparable to species that had leaves. Leaflessness status of sampled trees is not recorded in @Meinzer:2001. We therefore removed five species that are typically leafless in March-April (Joseph Wright, personal observation), that is, the months of $\mathrm{\delta}$^2^H~xylem~ sampling. $\mathrm{\delta}^2H$ to depth relationship was particularly uncertain for $\mathrm{\delta}^2H$ > -40 ‰, so from the remaining dataset, we removed one species, *Guapira standleyana*, with $\mathrm{\delta}$^2^H~xylem~ of -28.9 ‰ $\pm$ 3.7SE (see Fig. S3). For each model of ERD (Eq. \@ref(eq:M-chosen) and alternatives in SI), modeled species ERD was regressed against species $\mathrm{\delta}$^2^H~xylem~ for a maximum of six species.
